method

### 2021-10-15 06_Paper/ER-ED/method.Rmd
updated electromyography

Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (XX mm diameter, XX distance between electrodes) filled with electrolyte gel were used.
[...] <!-- Anne tried to implement a sentence here. -->

>>>>

Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. <!-- Stimmt das in etwa, liebe Anne? -->
[...] <!-- Anne tried to implement a sentence here. -->
